---
output:
  github_document: default
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# natalia

<!-- badges: start -->

<!-- badges: end -->

The goal of this package is to support me (Natalia) with my various Data Science tasks.

In practice, this is just an eclectic collection of personal functions that I keep on coming back to.
In the future, some of the functions might get migrated to their own niche packages where I'm sure they'll feel more at home!

<!--# TODO: add a hex sticker to left of this intro {hexSticker} -->

## Installation

You can install `natalia` from github with:

``` r
# install.packages("remotes")
# remotes::install_github("natalia-mlad/natalia")
```

## Examples

<!-- (maybe further broken down by usecases) -->

Here are some basic examples of how to use the functions found in this package:

```{r example}
library(natalia)
```

- ID ordinal variables from numeric ones

The following example is based on a cut-off point of 5, the max number of levels allowed for the variable before it stops being considered ordinal and becomes continuous.

```{r}
isOrd(mtcars, n = 5)
```

- Polytomize item data

For instance, you could simplify Likert item data into three categories for reporting or to use in further modeling.

```{r}
responses <- data.frame(
  item1 = sample(1:7, 50, replace = TRUE),
  item2 = sample(1:7, 50, replace = TRUE),
  item3 = sample(1:7, 50, replace = TRUE)
)
head(responses)
```


```{r}
polytomize_data(responses, thresholds = c(3,4)) %>%
  head()
```

- Scrape duckduckgo search results

This is useful for comparing top results and their sentiment across search enginges.

```{r, cache=TRUE}
duckduckgo(c("personal", "data", "privacy")) %>%
  head()
```

And so much more! (over 40 functions)
